smooth-sea

### 2018-05-29 index.rmd
updated version for presentation, fixed spt to follow INLA google group's discussion about obs-specific REs

m.spt <- inla(form.spt, 
              family = "normal", 
              data = sea_df,
              control.predictor = list(compute = TRUE),
              control.compute = list(dic = TRUE, waic = TRUE))

>>>>

m.spt <- inla(form.spt, 
              family = "normal", 
              data = sea_df,
              control.predictor = list(compute = TRUE),
              control.compute = list(dic = TRUE, waic = TRUE),
              control.inla = list(correct = TRUE, correct.factor = 10))
